Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2001-01-01 paper.tex
Add nsns cosA distributions of intensity

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{cosA_distrib-intensity-250km-00deg}
  \caption{Angular distributions of fluxes for an observer on the rotation axis
    in the hypermassive neutron star configuration.}
  \label{fig:nsns_cosA_distrib_I_00deg}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{cosA_distrib-intensity-250km-90deg}
  \caption{Angular distributions of fluxes for an observer in the equatorial
    plane in the hypermassive neutron star configuration.}
  \label{fig:nsns_cosA_distrib_I_90deg}
\end{figure}
